---
title: "Exercise 1"
format: html
execute: 
  echo: true
editor: visual
---

## First exercise

3\)

a\) iii. is correct because even though in the baseline case females earn more, the interaction effect is negative, and if the GPA is sufficiently high (at least 3.5), men earn more.

b\)

```{r}
beta_0 <- 50
beta_1 <- 20
beta_2 <- 0.07
beta_3 <- 35
beta_4 <- 0.01
beta_5 <- -10
IQ <- 110
GPA <- 4
GEN <- 1

beta_0 + GPA * beta_1 + IQ * beta_2 + GEN * beta_3 + GPA * IQ * beta_4 + GPA * GEN * beta_5
```

c\) FALSE

In the interaction effect we multiply IQ with GPA. The resulting number is thus big, so a small coefficient is okay. Whether it is statistically significant depends on the standard deviation of the variable and the sample size. (t test)

6\) In the simple regression case we have

$$
\hat{y_i} = \hat{\beta _0} + \hat{\beta _1} x_i
$$

If we plug in $x_i = \bar{x}$ and use 3.4, we get:

$$
\hat{y_i} = \bar{y} - \hat{\beta _1} \bar{x} + \hat{\beta _1} \bar{x} = \bar{y}
$$

Thus the statement is proven.

11\)

a\)

```{r}
set.seed(1)
x = rnorm(100)
y = 2*x+rnorm(100)

reg_a <- lm(y~x+0)
summary(reg_a)
```

The coefficient is 1.9939, and it is significant, because the p value is very small.

b\)

```{r}
reg_b <- lm(x~y+0)
summary(reg_b)
```

The coefficient is 0.39, and it is significant, with t t and p value being the same as in the last case.
